How Important are Usage Examples in REST API Documentation?

### 2017-03-05 controlled_study.tex
participants table addded

Participants were recruited through online announcements posted on Twitter, Facebook, and software developer focused mailing lists.

>>>>

A total 26 participants from sixteen different companies and six different countries (Canada, USA, Germany, Ireland, Brazil, and,
Bangladesh) were recruited through online announcements posted on Twitter, Facebook, and software developer focused mailing lists. Table \ref{table:participants} shows a summary of the experience level of the participants on each group.

\begin{table}[!tbh]
  \caption{Participant Profile}
  \label{table:participants}

\begin{tabular}{|p{0.8in} p{.6in} p{0.7in} p{0.7in}|}

\hline
& & \textbf{Group 1} & \textbf{Group 2}\\
\hline
\multicolumn{2}{|l}{\textbf{Number of Participants}} & 16 (P1.1-P1.16) & 10 (P2.1-P2.10) \\
\hline
\multicolumn{4}{|l|}{\textbf{Industry Experience}} \\
& 1-5 years & 5 & 1 \\
& 5-10 years & 6 & 5 \\
& 10+ years & 5 & 4 \\
& Average & 9.1 & 10.6 \\
\hline

\multicolumn{4}{|l|}{\textbf{REST API Experience}} \\
&   1-3 years & 5 & 3 \\
&   3-5 years & 7 & 4 \\
&   5+ years & 4 & 3 \\
&   Average & 4.5 & 4 \\

\hline
\multicolumn{2}{|l}{\textbf{Number of Companies}} & 10 & 8 \\
\hline
\end{tabular}

\end{table}
